### 2015-01-19 src/methodology.Rnw
updates

In order to ensure that the operators that we added were not redundant,
we computed their operator subsumption matrix. This is given in
Table~\ref{tbl:subsumption}, and a visualization of the subsumption is
presented in Figure~\ref{fig:subsumption}. This shows that the operators
we used were non-redundant, with a maximum subsumption of only $40\%$.

% Figure~\ref{fig:op} shows
% the distribution of mutants and the relative detection rates of each
% mutation operator for our projects. In the figure, there are two box-plots
% corresponding to each mutation operator on the Y-axis. The black box represents
% the relative frequency of the particular mutation operator in the total
% mutants \textit{produced}. For example, for projects in the (Randoop) generated set,
% the operator \pitnvmc contributed about 34\% of the total number of mutants
% produced while \pitrv contributed about 7\%. Similarly, the blue shaded
% box-plot represents the relative frequency of particular mutation operator
% in the total mutants \textit{detected}. For example, \Pitnvmc contribution
% in the detected mutants was 23\% while that of \Pitrv was 15\%.

For a detailed description of each mutation operator, please refer to PIT documentation~\cite{pitmut}.
We modified PIT to report the entire test matrix of $tests \times failures$
rather than just the first failure, and used this for our analysis. To remove
the effects of random noice, results of each criteria was averaged out of ten
runs.

>>>>

In order to ensure that the operators that we added were not redundant,
we computed their operator subsumption matrix. This is given in
Table~\ref{tbl:subsumption}, and a visualization of the subsumption is
presented in Figure~\ref{fig:subsumption}. In the figure, the amount of
subsumption is indicated by removal of area from the circle, with same
operators subsuming themselves entirely. This suggests that the operators
we used were non-redundant, with a maximum subsumption of only $40\%$.
The Figure~\ref{fig:mutationshare} shows the share of each mutation operators
in the total number of mutants produced, and the Figure~\ref{fig:mutationkills}
shows the detection and covering rate of mutants by test cases.

For a detailed description of each mutation operator, please refer to PIT
documentation~\cite{pitmut}.  We modified PIT to report the entire test
matrix of $tests \times failures$ rather than just the first failure, and
used this for our analysis. To remove the effects of random noise, results
of each criteria was averaged out of ten runs.
